---
title: "Example report on synthetic data"
output: pdf_document
---

```{r setup, include=FALSE}
## Packages needed
packages <- c("tidyverse", "here", "ggplot2", "knitr", "kableExtra", "tidytext", "ggpubr")

## Write a function to install the packages if they haven't been installed,
## and to load the packages
install <- function(pack) {
  if(!requireNamespace(pack)) {
    install.packages(pack, repos = "https://cloud.r-project.org")
  }
}

## Run the funciton to install and load needed packages 
sapply(packages, install)
sapply(packages, require, character.only = T)


# Read data

here::here()

## Statisitcal methodology checkbox and subquestions
#stat <- read_csv("../Data/Statistical Methodology Needs.csv")
load("../Data/Processed/Statistical_Methodology_Needs.RDATA")

## Software engineering checkbox and subquestions
#soft <- read_csv("../Data/Software Engineering Needs.csv")
load("../Data/Processed/Software_Engineering_Needs.RDATA")

## Other questions
load("../Data/Processed/Other_Questions.RDATA")
```



```{r function, include=FALSE}
# Function creating the frequency table

freq_table <- function(tab, var_name, 
                       transform = FALSE, ordered = FALSE,
                       caption = NULL, width_col1 = NULL, width_col2 = NULL, longtable = F, position = "HOLD_position") {
  
  # tab is a data frame with frequency, 
  # or a vector that needs to be transformed into frequency table
  
  if (transform) {
    tab <- as.data.frame(table(tab))
  }
  
  if (ordered) {
    tab <- tab[order(tab[, 2], decreasing = T), ]
  }
  
  tab %>%
    kable(booktabs = T,
          caption = caption, col.names = c(var_name, "N"), row.names = F, longtable = longtable) %>%
    kable_styling(latex_options = "striped") %>%
    kable_styling(latex_options = position) %>%
    column_spec(column = 1, width = width_col1) %>%
    column_spec(column = 2, width = width_col2) %>%
    row_spec(0, bold = T)
    
}



# Function capitalizing the first letter in the phrase
capital <- function(x, word1_only = F) {
  
  if (word1_only) {
    s <- x
    X <- NA
    for (i in 1:length(s)) {
      X[i] <- paste0(toupper(substring(s[[i]], 1,1)), substring(s[[i]], 2))
    } 
  } else {
    s <- strsplit(x, " ")
    X <- NA
    for (i in 1:length(s)) {
      X[i] <- paste(toupper(substring(s[[i]], 1,1)), substring(s[[i]], 2),
        sep="", collapse=" ")
    }
  }
  
  
  return(X)
}


four_tables = function(f1, f2, f3, f4){
    # Setting `results = 'asis'` allows for using Latex within the code chunk
    cat('\\begin{center}')
    cat('\\begin{tabular}{ c c }')
    print(knitr::kable(table(f1), booktabs = T,  format = 'latex', col.names = c("Frequency of Needs", "N")) %>% row_spec(0, bold = T))
    cat('&')
    print(knitr::kable(table(f2), booktabs = T, format = 'latex', col.names = c("Severity of Needs", "N")) %>% row_spec(0, bold = T))
    cat('\\end{tabular}')
    cat('\\end{center}')
    cat('\\begin{center}')
    cat('\\begin{tabular}{ c c }')
    print(knitr::kable(table(f3),booktabs = T,  format = 'latex', col.names = c("Difficulty to Support Needs", "N")) %>% row_spec(0, bold = T))
    cat('&')
    print(knitr::kable(table(f4), booktabs = T, format = 'latex', col.names = c("Difficulty to Find Help", "N")) %>% row_spec(0, bold = T))
    cat('\\end{tabular}')
    cat('\\end{center}')
}

```



```{r number of participants, include=FALSE}
n_participant <- nrow(other)
```


```{r number of schools, include = FALSE}
# School

schools <- other %>%
  
  # Select relevant variables and drop rows with missing school
  select(id, school, school_selfenter) %>%
  filter(!is.na(school)) %>%
  
  # Unnest the schools  
  unnest_tokens(output = school, input = school, token = 'regex', pattern=",", to_lower = FALSE) %>%
  
  # Add a column of the grouped "other" categories,
  # and replace the "other" in the school variable with the grouped other categories
  mutate(school_selfenter_g = case_when(school_selfenter=="Gallatin School of Individualized Study" ~ "Gallatin",
                                        school_selfenter=="NYU Student Health Center" ~ "Student Health Center",
                                        TRUE ~ school_selfenter),
         
         school = ifelse(school=="other", school_selfenter_g, school)) %>%

  # Compute the number of participants of each school
  group_by(school) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  arrange(-n)

n_schools = dim(schools)[[1]]
```

This report is based on **synthetic** data from `r n_participant` participants representing affiliations with `r n_schools` schools or centers across the university.

Our respondents were affiliated with the following schools and varied in their rank:

```{r, echo=FALSE}
# School
schools <- other %>%
  
  # Select relevant variables and drop rows with missing school
  select(id, school, school_selfenter) %>%
  filter(!is.na(school)) %>%
  
  # Unnest the schools  
  unnest_tokens(output = school, input = school, token = 'regex', pattern=",", to_lower = FALSE) %>%
  
  # Add a column of the grouped "other" categories,
  # and replace the "other" in the school variable with the grouped other categories
  mutate(school_selfenter_g = case_when(school_selfenter=="Gallatin School of Individualized Study" ~ "Gallatin",
                                        school_selfenter=="NYU Student Health Center" ~ "Student Health Center",
                                        TRUE ~ school_selfenter),
         
         school = ifelse(school=="other", school_selfenter_g, school)) %>%

  # Compute the number of participants of each school
  group_by(school) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  arrange(-n) 
  

# Table and Barplot
freq_table(schools[, c("school", "n")], "School", caption = "Number of Participants in Different Schools")

# ggplot(schools, aes(x = reorder(school, -n), y = n)) +
#   geom_bar(stat = "identity") +
#   theme(axis.text.x = element_text(angle = 60, hjust = 1),
#         plot.title = element_text(hjust = 0.5)) +
#   ggtitle("Number of Participants in Different Schools") +
#   xlab("School") + ylab("N") 
```

```{r, echo=FALSE}
# Rank 
# Rank 

ranks <- other %>%
  
  # Select relevant variables and drop rows with missing school
  select(id, rank, rank_selfenter) %>%
  filter(!is.na(rank)) %>%
  
  # Unnest the schools  
  unnest_tokens(output = rank, input = rank, token = 'regex', pattern=",", to_lower = FALSE) %>%
  
  # Add a column of the grouped "other" categories,
  # and replace the "other" in the rank variable with the grouped other categories
 
  ## The following code line is just an example of grouping / renaming other ranks, 
  ## and it should be adjusted according to the actual data.
  ## The next chunk {r other rank} provides to codes to see all the self-entered other ranks
  ## which can be used for the grouping
  mutate(rank_selfenter_g = case_when(tolower(rank_selfenter) %in% c("research scholar", "ft research staff", "research fellow", "research staff") ~ "Research Staff / Fellow",
                                      tolower(rank_selfenter) %in% c("center director", "executive director of a center") ~ "Director",
                                      TRUE ~ rank_selfenter),
         
         rank = ifelse(rank=="other", rank_selfenter_g, rank)) %>%

  # Compute the number of participants of each school
  group_by(rank) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  arrange(-n) %>%
  
  # Capitalize all the ranks
  mutate(rank = capital(rank))
  

# Table and Barplot
freq_table(ranks[, c("rank", "n")], "Rank", caption = "Number of Participants of Different Ranks", position = c("HOLD_position", "repeat_header"), longtable = T)

```

# Statistical Methodology

We asked respondents: Which of the following Statistical Methodology do you currently use in your work, need help with, or expect that you may need help with in the future? Respondents indicated:

```{r, echo=FALSE}
# Group the "Other" categories 
# and replace the "Other" in the stat_need variable with the grouped other categories

stat <- stat %>%
  
  ## The following code line is just an example of grouping / renaming other statistical methodologies, 
  ## and it should be adjusted according to the actual data.
  ## The next chunk {r other stat} provides to codes to see all the self-entered other stat methods
  ## which can be used for the grouping
  mutate(stat_need_selfenter_g = case_when(stat_need_selfenter %in% c("None", "none of the above") ~ "",
                                           stat_need_selfenter %in% c("large scale simulations") ~ "Simulation", 
                                           stat_need_selfenter %in% c("otherstat") ~ "Other", 
                                           TRUE ~ stat_need_selfenter)) %>%
         
         mutate(stat_need = ifelse(stat_need %in% c("Other", ""), stat_need_selfenter_g, stat_need)) 


stat_needs <- stat %>%
  
  # Select relevant variables and drop rows with missing stat_need
  select(id, stat_need) %>%
  filter(stat_need != "") %>%

  # Compute the number of participants of each statistical methodology
  group_by(stat_need) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  arrange(-n) %>%
  
  mutate(stat_need = capital(stat_need))


# Table and barplot
freq_table(stat_needs[, c("stat_need", "n")], "Statistical Methodology", caption = "Statistical Methodology in Need")

```


```{r other stat, echo=FALSE, results='hide'}
other_stat <- stat %>%
  filter(stat_need_selfenter != "") %>%
  distinct(id, stat_need_selfenter) %>%
  select(stat_need_selfenter)

if (length(other_stat) > 0) {
  freq_table(other_stat, "Other Stat Method", transform = T, ordered = T)
}
```


Once a type of statistical methodology was selected, four sub-questions were posed pertaining to how much the respondent needed that particular skill. These questions were: 

1. How often do you currently need to perform these tasks in your research?

2. To what extent do you think access to people who could help you with these tasks would help your research?

3. How hard is it for you to currently support someone to help you with these tasks through your grants?

4. How hard is it for you to currently find people to help you with these tasks?

The following pages outline how respondents answered each of these four questions, first in aggregate over all statistical methodology needs, and then with regards to each needed skill.


```{r, results = 'asis', echo=FALSE}
# Aggregated table and plot
print(kable(paste0("Statistical Methodology In General"), "latex", col.names = NULL, booktabs = T) %>% row_spec(1, bold = T) %>% kable_styling(position = "center"))

four_tables(stat$need_freq, stat$help_extent, stat$support_difficulty, stat$find_difficulty)

p1 <- ggplot(stat, aes(x = need_freq)) +
      geom_bar() + ggtitle("Frequency of Need") +
      theme(axis.text.x = element_text(size = 7), axis.title.x=element_blank(), axis.title.y = element_blank()) +
      scale_x_discrete(drop=FALSE)
  
p2 <- ggplot(stat, aes(x = help_extent)) +
      geom_bar() + ggtitle("Severity of Need") +
      theme(axis.text.x = element_text(size = 7), axis.title.x=element_blank(), axis.title.y = element_blank()) +
      scale_x_discrete(labels = c("Critical to research" = "Critical",
                                  "Greatly help" = "Greatly",
                                  "Moderately help" = "Moderately",
                                  "Slightly help" = "Slightly",
                                  "Not at all" = "None"),
                       drop=FALSE)
  
p3 <- ggplot(stat, aes(x = support_difficulty)) +
      geom_bar() + ggtitle("Difficulty to Support Needs") +
      theme(axis.title.x=element_blank(), axis.title.y = element_blank()) +
      scale_x_discrete(drop=FALSE)
  
p4 <- ggplot(stat, aes(x = find_difficulty)) +
      geom_bar() + ggtitle("Difficulty to Find Help") +
      theme(axis.title.x=element_blank(), axis.title.y = element_blank()) +
      scale_x_discrete(drop=FALSE)

p <- ggarrange(p1, p2, p3, p4, ncol = 2, nrow = 2)
p
```

\pagebreak


```{r, echo=FALSE, results='asis'}
# Here we set the minimum number of respondents to be 5 for each statistical methodology, if we want to show the table and plot for that statistical methodology
# This number can be adjusted according to the actual number of respondents in the real survey
min_resp <- 5


m <- unique(stat_needs$stat_need)

for (i in 1:length(m)) {
  
  stat_method <- stat[tolower(stat$stat_need) == tolower(m[i]), ]
  
  # If there are more than 5 respondents for the statistical methodology,
  # then show the tables and plots of the subquestions
  
  if (stat_needs$n[i] >= min_resp) {
    
  print(kable(paste0(m[i], ":"), "latex", col.names = NULL, booktabs = T) %>% row_spec(1, bold = T) %>% kable_styling(position = "center"))
  
  four_tables(stat_method$need_freq, stat_method$help_extent, stat_method$support_difficulty, stat_method$find_difficulty)


    p1 <- ggplot(stat_method, aes(x = need_freq)) +
      geom_bar() + ggtitle("Frequency of Need") +
      theme(axis.text.x = element_text(size = 7), axis.title.x=element_blank(), axis.title.y = element_blank()) +
      scale_x_discrete(drop=FALSE)
  
    p2 <- ggplot(stat_method, aes(x = help_extent)) +
      geom_bar() + ggtitle("Severity of Need") +
      theme(axis.text.x = element_text(size = 7), axis.title.x=element_blank(), axis.title.y = element_blank()) +
      scale_x_discrete(labels = c("Critical to research" = "Critical",
                                  "Greatly help" = "Greatly",
                                  "Moderately help" = "Moderately",
                                  "Slightly help" = "Slightly",
                                  "Not at all" = "None"),
                       drop=FALSE)
  
    p3 <- ggplot(stat_method, aes(x = support_difficulty)) +
      geom_bar() + ggtitle("Difficulty to Support Needs") +
      theme(axis.title.x=element_blank(),axis.title.y = element_blank()) +
      scale_x_discrete(drop=FALSE)
  
    p4 <- ggplot(stat_method, aes(x = find_difficulty)) +
      geom_bar() + ggtitle("Difficulty to Find Help") +
      theme(axis.title.x=element_blank(),axis.title.y = element_blank()) +
      scale_x_discrete(drop=FALSE)
  
    print(ggarrange(p1, p2, p3, p4, ncol = 2, nrow = 2))
    
    cat("\\pagebreak")
  }
  
}
```

Respondents were asked which best described their opinion about supporting your statistical methodology needs through grants? Faculty identified barriers to being able to hire talent even if they can (partially) support it through grants.

```{r, echo=F}
freq_table(other$stat_opinion_support, "", 
           transform = T, width_col1 = "15cm",
           caption = "Opinion about supporting statistical methodology needs through grants")
```

```{r, echo = F, fig.width = 6, fig.height = 4, fig.align = 'center'}
ggplot(other[!is.na(other$stat_opinion_support), ], aes(x = stat_opinion_support)) +
  geom_bar() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(labels = c("Not need", 
                              "Possible to hire \n through grants \n on my own", 
                              "Able to support, \n but difficult to hire \n skilled people", 
                              "Can only partially \n support",
                              "Unlikely to support"),
                   drop = FALSE) +
  ggtitle("Opinion about Supporting \n Statistical Methodology Needs through Grants") +
  xlab("") + ylab("")
```

Next, we asked respondents whether, if there was a university-selected pool of people available to contract, they would be interested in contracting services from a university pool.

```{r, echo=F}
freq_table(other$stat_univers_pool, "", 
           transform = T, width_col1 = "15cm",
           caption = "Opinion about contracting statistical methodology services from a university pool")
```


```{r, echo=F, warning = F}
stat_accesses <- other %>%
  
  select(id, stat_access, stat_access_other_specify) %>%
  
  # Unnest the accesses
  unnest_tokens(output = stat_access, input = stat_access, token = 'regex', pattern=",", to_lower = FALSE) %>%
  
  # Group the "other" categories
  
  ## The following code line is just an example of grouping / renaming other accesses, 
  ## and it should be adjusted according to the actual data.
  ## The next chunk {r other stat access} provides to codes to see all the self-entered other accesses
  ## which can be used for the grouping
  mutate(stat_access_other_specify_g = case_when(
    stat_access_other_specify %in% c("Do it myself", "I'm a biostatistician") ~ "Do it myself",
    stat_access_other_specify %in% c("Consult within the school") ~ "Consult / hire within school",
    TRUE ~ stat_access_other_specify
    )) %>%
  
  # Replace the category of other
  mutate(stat_access = ifelse(stat_access=="Other (Please specify which:)", stat_access_other_specify_g, stat_access),
         stat_access = ifelse(stat_access=="Seek consultation from outside the university (Please specify which:)", "Seek consultation from outside the university", stat_access)) %>%
  
  # Compute the number of participants of each access
  group_by(stat_access) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  filter(stat_access != "") %>%
  arrange(-n) %>%
  
  # Capitalize the first letter
  mutate(stat_access = capital(stat_access, word1_only = T))
 

# Table and barplot 
  
freq_table(stat_accesses, "Access", caption = "How to Access Statistical Services")

```


```{r, echo=FALSE, results='hide', warning = F}
other_access <- other$stat_access_other_specify[other$stat_access_other_specify!=""]

if (length(other_access) > 0) {
  freq_table(other_access, "Other Access", transform = T, ordered = T)
}
```


The following table shows where respondents go when they seek consultation from outside the university.

```{r, echo=F}
other$stat_access_consult_specify[other$stat_access_consult_specify!=""] %>% kable(caption = "Source of Outside Statistical Consultation", 
        col.names = NULL, row.names = F, longtable = T, booktabs = T) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header")) %>%
  kable_styling(latex_options = "striped") %>%
  column_spec(column = 1, width = "15cm")

```

In order to better understand where in the research life cycle such help would be needed, we asked respondents to indicate when they usually required statistical consulting services and why they were seeking out help.

```{r, echo=F}
freq_table(other$stat_need_when, "", transform = T,
           caption = "When Do You Rely on Statistical Services?")

```

```{r, echo=F}
freq_table(other$stat_need_reason, "", transform = T,
           caption = "Why Do You Need Statistical Services?", width_col1 = "15cm")

```

With regards to statistical methodology support, a final set of questions were asked relating to the number of full time equivalents (FTEs) that the respondent would potentially need and potentially be able to support. The following summaries indicate that only a fraction of the expected needs can currently be met.

```{r, echo=F}
# FTE needed
stat_FTE_needs <- other %>%
  filter(!is.na(stat_FTE_need)) %>%
  mutate(stat_FTE_need = factor(stat_FTE_need)) %>%
  group_by(stat_FTE_need) %>%
  summarise(N = n()) %>%
  ## weighted sum
  mutate(ws = sum(as.numeric(as.character(stat_FTE_need)) * N))


# FTE supported
stat_FTE_supports <- other %>%
  filter(!is.na(stat_FTE_support)) %>%
  mutate(stat_FTE_support = factor(stat_FTE_support)) %>%
  group_by(stat_FTE_support) %>%
  summarise(N = n()) %>%
  ## weighted sum
  mutate(ws = sum(as.numeric(as.character(stat_FTE_support)) * N))
```

```{r, echo=F}
data.frame(FTE_Needed = stat_FTE_needs$ws[1], FTE_Supported = stat_FTE_supports$ws[1],
           Needs_Supports_Gap = stat_FTE_needs$ws[1] - stat_FTE_supports$ws[1],
           Pct_Needs_Supported = paste0(round(stat_FTE_supports$ws[1] / stat_FTE_needs$ws[1] * 100, 1), "%")) %>%
  kable(booktabs = T,
        caption = "Gap Between Statistical FTE Needed and FTE Potentially Supported", col.names = c("Needed", "Potentially Supported", "Gap", "% Potentially Supported"), row.names = F) %>%
    kable_styling(latex_options = "striped") %>%
    kable_styling(latex_options = "HOLD_position") %>%
    row_spec(0, bold = T)
```


```{r, echo=F}
# # Difference between FTE needed and FTE supported (Q3 - Q4)
 stat_FTE_diff <- other$stat_FTE_need - other$stat_FTE_support
```

\pagebreak

# Software Engineering


We similarly asked respondents which of the following aspects of software engineering  do you currently use in your work, need help with, or expect that you may need help with in the future. Respondents indicated:

```{r, echo=FALSE}
# Group the "Other" categories 
# and replace the "Other" in the soft_need variable with the grouped other categories
soft <- soft %>%
  
  ## The following code line is just an example of grouping / renaming other software engineering, 
  ## and it should be adjusted according to the actual data.
  ## The next chunk {r other soft} provides to codes to see all the self-entered other software engineering
  ## which can be used for the grouping
  mutate(soft_need_selfenter_g = case_when(soft_need_selfenter %in% c("none", "none of the above") ~ "",
                                           soft_need_selfenter == "Spark and Hadoop tools programming" ~ "Spark & Hadoop",
                                           TRUE ~ soft_need_selfenter)) %>%
  
  mutate(soft_need = ifelse(soft_need %in% c("Other", ""), soft_need_selfenter_g, soft_need))


# Prepare the frequency data frame
soft_needs <- soft %>%
  
  # Select relevant variables and drop rows with missing soft_need
  select(id, soft_need) %>%
  filter(soft_need != "") %>%

  # Compute the number of participants of each school
  group_by(soft_need) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  arrange(-n) %>%
  
  mutate(soft_need = capital(soft_need))


# Table and barplot

freq_table(soft_needs[, c("soft_need", "n")], "Software Engineering", caption = "Software Engineering in Need")
```


```{r other soft, echo=FALSE, results='hide'}
other_soft <- soft %>%
  filter(soft_need_selfenter != "") %>%
  distinct(id, soft_need_selfenter) %>%
  select(soft_need_selfenter)

if (length(other_soft) > 0) {
  freq_table(other_soft, "Other Software Engineering", transform = T, ordered = T)
}
```



Once an aspect of software engineering  was selected, four sub-questions were posed pertaining to how much the respondent needed that particular skill. These questions were: 
  
  1. How often do you currently need to perform these tasks in your research?
  
  2. To what extent do you think access to people who could help you with these tasks would help your research?
  
  3. How hard is it for you to currently support someone to help you with these tasks through your grants?
  
  4. How hard is it for you to currently find people to help you with these tasks?
  
  The following pages outline how respondents answered each of these four questions, first in aggregate over all software engineering needs, and then with regards to each needed aspect.
  
  \pagebreak
```{r, results = 'asis', echo=FALSE}
# Aggregated table and plot
print(kable(paste0("Software Engineering In General"), "latex", col.names = NULL, booktabs = T) %>% row_spec(1, bold = T) %>% kable_styling(position = "center"))

four_tables(soft$need_freq, soft$help_extent, soft$support_difficulty, soft$find_difficulty)

p1 <- ggplot(soft, aes(x = need_freq)) +
  geom_bar() + ggtitle("Frequency of Need") +
  theme(axis.text.x = element_text(size = 7), axis.title.x=element_blank(), axis.title.y = element_blank()) +
  scale_x_discrete(drop=FALSE)

p2 <- ggplot(soft, aes(x = help_extent)) +
  geom_bar() + ggtitle("Severity of Need") +
  theme(axis.text.x = element_text(size = 7), axis.title.x=element_blank(), axis.title.y = element_blank()) +
  scale_x_discrete(labels = c("Critical to research" = "Critical",
                              "Greatly help" = "Greatly",
                              "Moderately help" = "Moderately",
                              "Slightly help" = "Slightly",
                              "Not at all" = "None"),
                   drop=FALSE)

p3 <- ggplot(soft, aes(x = support_difficulty)) +
  geom_bar() + ggtitle("Difficulty to Support Needs") +
  theme(axis.title.x=element_blank(), axis.title.y = element_blank()) +
  scale_x_discrete(drop=FALSE)

p4 <- ggplot(soft, aes(x = find_difficulty)) +
  geom_bar() + ggtitle("Difficulty to Find Help") +
  theme(axis.title.x=element_blank(), axis.title.y = element_blank()) +
  scale_x_discrete(drop=FALSE)

p <- ggarrange(p1, p2, p3, p4, ncol = 2, nrow = 2)
p
```


\pagebreak

```{r, echo = F, results='asis'}
# Here we set the minimum number of respondents to be 5 for each software engineering task, if we want to show the tables and plots for that software engineering task
# This number can be adjusted according to the actual number of respondents in the real survey
min_resp <- 5


m <- unique(soft_needs$soft_need)

for (i in 1:length(m)) {
  
  soft_method <- soft[tolower(soft$soft_need) == tolower(m[i]), ]
  
  # If there are more than 5 respondents for the software engineering,
  # then show the tables and plots of the subquestions
  
  if (soft_needs$n[i] >= min_resp) {
    
    print(kable(paste0(m[i], ":"), "latex", col.names = NULL, booktabs = T) %>% row_spec(1, bold = T) %>% kable_styling(position = "center"))
    
    four_tables(soft_method$need_freq, soft_method$help_extent, soft_method$support_difficulty, soft_method$find_difficulty)

    
    p1 <- ggplot(soft_method, aes(x = need_freq)) +
      geom_bar() + ggtitle("Frequency of Need") +
      theme(axis.text.x = element_text(size = 7), axis.title.x=element_blank(), axis.title.y = element_blank()) +
      scale_x_discrete(drop=FALSE)
    
    p2 <- ggplot(soft_method, aes(x = help_extent)) +
      geom_bar() + ggtitle("Severity of Need") +
      theme(axis.text.x = element_text(size = 7), axis.title.x=element_blank(), axis.title.y = element_blank()) +
      scale_x_discrete(labels = c("Critical to research" = "Critical",
                                  "Greatly help" = "Greatly",
                                  "Moderately help" = "Moderately",
                                  "Slightly help" = "Slightly",
                                  "Not at all" = "None"),
                       drop=FALSE)
    
    p3 <- ggplot(soft_method, aes(x = support_difficulty)) +
      geom_bar() + ggtitle("Difficulty to Support Needs") +
      theme(axis.title.x=element_blank(),axis.title.y = element_blank()) +
      scale_x_discrete(drop=FALSE)
    
    p4 <- ggplot(soft_method, aes(x = find_difficulty)) +
      geom_bar() + ggtitle("Difficulty to Find Help") +
      theme(axis.title.x=element_blank(),axis.title.y = element_blank()) +
      scale_x_discrete(drop=FALSE)
    
    print(ggarrange(p1, p2, p3, p4, ncol = 2, nrow = 2))
    
    cat("\\pagebreak")
  }
  
}
```

Respondents were asked which best described their opinion about supporting your software engineering needs through grants? Faculty identified barriers to being able to hire talent even if they can (partially) support it through grants.

```{r, echo=F}
freq_table(other$soft_opinion_support, "", 
           transform = T, width_col1 = "15cm",
           caption = "Opinion about supporting software engineering needs through grants")
```

```{r, echo = F, fig.width = 6, fig.height = 4, fig.align = 'center'}
ggplot(other[!is.na(other$soft_opinion_support), ], aes(x = soft_opinion_support)) +
  geom_bar() +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_discrete(labels = c("Not need", 
                              "Possible to hire \n through grants \n on my own", 
                              "Able to support, \n but difficult to hire \n skilled people", 
                              "Can only partially \n support",
                              "Unlikely to support"),
                   drop = FALSE) +
  ggtitle("Opinion about Supporting \n Software Engineering Needs through Grants") +
  xlab("") + ylab("")
```

Next, we asked respondents whether, if there was a university-selected pool of people available to contract, they would be interested in contracting services from a university pool.

```{r, echo=F}
freq_table(other$soft_univers_pool, "", 
           transform = T, width_col1 = "15cm",
           caption = "Opinion about contracting software engineering services from a university pool")
```

We further queried the respondents about how they currently meet their software needs. 


```{r, echo=F, warning = F}
soft_accesses <- other %>%
  
  select(id, soft_access, soft_access_other_specify) %>%
  
  # Unnest the accesses
  unnest_tokens(output = soft_access, input = soft_access, token = 'regex', pattern=",", to_lower = FALSE) %>%
  
  # Group the "other" categories
  
  ## The following code line is just an example of grouping / renaming other accesses, 
  ## and it should be adjusted according to the actual data.
  ## The next chunk {r other soft access} provides to codes to see all the self-entered other accesses
  ## which can be used for the grouping
  mutate(soft_access_other_specify_g =  case_when(
    soft_access_other_specify %in% c("Do it myself") ~ "Do it myself",
    soft_access_other_specify %in% c("hire a software engineer") ~ "Hire software staff",
    soft_access_other_specify == "other1" ~ "Other",
    TRUE ~ soft_access_other_specify
    )) %>%
  
  # Replace the category of other
  mutate(soft_access = ifelse(soft_access=="Other (Please specify which:)", soft_access_other_specify_g, soft_access),
         soft_access = ifelse(soft_access=="Seek consultation from outside the university (Please specify which:)", "Seek consultation from outside the university", soft_access)) %>%
  
  # Compute the number of participants of each access
  group_by(soft_access) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  filter(soft_access != "") %>%
  arrange(-n) %>%
  
  # Capitalize the first letter
  mutate(soft_access = capital(soft_access, word1_only = T))



# Table and barplot 
  
freq_table(soft_accesses, "Access", caption = "How to Access Software Services")

ggplot(soft_accesses, aes(x = reorder(soft_access, -n), y = n)) +
  geom_bar(stat = "identity") +
  theme(plot.title = element_text(hjust = 0.5), 
        axis.text.x = element_text(angle = 60, hjust = 1)) +
  scale_x_discrete(labels = c("I don’t" = "Not access", 
                              "Seek consultation from outside the university" = "Outside consultation",
                              "Have a stat collaborator I brought with mr" = "Stat collaborator",
                              "NYU Library Data Services Lab" = "Data Services")) +
  ggtitle("How Participants Access to Software Engineering Services") +
  xlab("Access") + ylab("N")
```

In order to better understand where in the research life cycle such help would be needed, we asked respondents to indicate when they usually required software consulting services and why they were seeking out help.

```{r, echo=F}
freq_table(other$soft_need_when, "", transform = T,
           caption = "When Do You Rely on Software Services?")
```

```{r, echo=F}
freq_table(other$soft_need_reason, "", transform = T,
           caption = "Why Do You Need Software Services?", width_col1 = "15cm")
```

With regards to software engineering support, a final set of questions were asked relating to the number of full time equivalents (FTEs) that the respondent would potentially need and potentially be able to support. The following summaries indicate that only a fraction of the expected needs can currently be met.

```{r, echo=F}
# FTE needed
soft_FTE_needs <- other %>%
  filter(!is.na(soft_FTE_need)) %>%
  mutate(soft_FTE_need = factor(soft_FTE_need)) %>%
  group_by(soft_FTE_need) %>%
  summarise(N = n()) %>%
  ## weighted sum
  mutate(ws = sum(as.numeric(as.character(soft_FTE_need)) * N))


# FTE supported
soft_FTE_supports <- other %>%
  filter(!is.na(soft_FTE_support)) %>%
  mutate(soft_FTE_support = factor(soft_FTE_support)) %>%
  group_by(soft_FTE_support) %>%
  summarise(N = n()) %>%
  ## weighted sum
  mutate(ws = sum(as.numeric(as.character(soft_FTE_support)) * N))
```


```{r, echo=F}
data.frame(FTE_Needed = soft_FTE_needs$ws[1], FTE_Supported = soft_FTE_supports$ws[1],
           Needs_Supports_Gap = soft_FTE_needs$ws[1] - soft_FTE_supports$ws[1],
           Pct_Needs_Supported = paste0(round(soft_FTE_supports$ws[1] / soft_FTE_needs$ws[1] * 100, 1), "%")) %>%
  kable(booktabs = T,
        caption = "Gap Between Software FTE Needed and FTE Potentially Supported", col.names = c("Needed", "Potentially Supported", "Gap", "% Potentially Supported"), row.names = F) %>%
  kable_styling(latex_options = "striped") %>%
  kable_styling(latex_options = "HOLD_position") %>%
  row_spec(0, bold = T)
```


```{r, echo=F}
# # Difference between FTE needed and FTE supported (Q3 - Q4)
soft_FTE_diff <- other$soft_FTE_need - other$soft_FTE_support
```

```{r, fig.width = 3, fig.height = 3, fig.align = 'center', echo = F}
ggplot(data.frame(dif = soft_FTE_diff[!is.na(soft_FTE_diff)]), aes(x = factor(dif))) +
  geom_bar() +
  theme(plot.title = element_text(hjust = 0.5)) +
  ggtitle("Gap Between Needed and \n Potentially Supported FTEs") +
  xlab("FTE difference") + ylab("")
```



# Open-ended Questions

```{r, echo=F}
oe_public <- other %>%
  filter(willing_quote == "")
```

### Other things you would like us to know?

```{r, echo=F}
oe_public %>%
  filter(other_experience != "") %>%
  select(other_experience) %>%
  kable(caption = "Other Experience (For Public Use)", 
        col.names = NULL, row.names = F, longtable = T) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header")) %>%
  column_spec(column = 1, width = "15cm")
```

### Any other comments?

```{r, echo=F}
oe_public %>%
  filter(other_comment != "") %>%
  select(other_comment) %>%
  kable(caption = "Other Comments (For Public Use)", 
        col.names = NULL, row.names = F, longtable = T) %>%
  kable_styling(latex_options = c("HOLD_position", "repeat_header")) %>%
  column_spec(column = 1, width = "15cm")
```


