---
title: "Statistical and Software Needs at NYU"
output: pdf_document
---

```{r setup, include=FALSE}
## Packages needed
packages <- c("tidyverse", "here", "ggplot2", "knitr", "kableExtra", "tidytext", "ggpubr")

## Write a function to install the packages if they haven't been installed,
## and to load the packages
install <- function(pack) {
  if(!requireNamespace(pack)) {
    install.packages(pack, repos = "https://cloud.r-project.org")
  }
}

## Run the funciton to install and load needed packages 
sapply(packages, install)
sapply(packages, require, character.only = T)


# Read data

here::here()

## Statisitcal methodology checkbox and subquestions
#stat <- read_csv("../Data/Statistical Methodology Needs.csv")
load("../Data/Processed/Statistical Methodology Needs.RDATA")

## Software engineering checkbox and subquestions
#soft <- read_csv("../Data/Software Engineering Needs.csv")
load("../Data/Processed/Software Engineering Needs.RDATA")

## Other questions
load("../Data/Processed/Other Questions.RDATA")
```



```{r function, include=FALSE}
# Function creating the frequency table

freq_table <- function(tab, var_name, 
                       transform = FALSE, ordered = FALSE,
                       caption = NULL, width_col1 = NULL, width_col2 = NULL) {
  
  # tab is a data frame with frequency, 
  # or a vector that needs to be transformed into frequency table
  
  if (transform) {
    tab <- as.data.frame(table(tab))
  }
  
  if (ordered) {
    tab <- tab[order(tab[, 2], decreasing = T), ]
  }
  
  tab %>%
    kable(booktabs = T,
          caption = caption, col.names = c(var_name, "N"), row.names = F) %>%
    kable_styling(latex_options = "striped") %>%
    kable_styling(latex_options = "HOLD_position") %>%
    column_spec(column = 1, width = width_col1) %>%
    column_spec(column = 2, width = width_col2) %>%
    row_spec(0, bold = T)
    
}

```

```{r include = FALSE}



# Function capitalizing the first letter in the phrase
capital <- function(x, word1_only = F) {
  
  if (word1_only) {
    s <- x
    X <- NA
    for (i in 1:length(s)) {
      X[i] <- paste0(toupper(substring(s[[i]], 1,1)), substring(s[[i]], 2))
    } 
  } else {
    s <- strsplit(x, " ")
    X <- NA
    for (i in 1:length(s)) {
      X[i] <- paste(toupper(substring(s[[i]], 1,1)), substring(s[[i]], 2),
        sep="", collapse=" ")
    }
  }
  
  
  return(X)
}
```


```{r number of participants, include=FALSE}
n_participant <- nrow(other)
```

```{r number of schools, include = FALSE}
# School

schools <- other %>%
  
  # Select relevant variables and drop rows with missing school
  select(id, school, school_selfenter) %>%
  filter(!is.na(school)) %>%
  
  # Unnest the schools  
  unnest_tokens(output = school, input = school, token = 'regex', pattern=",", to_lower = FALSE) %>%
  
  # Add a column of the grouped "other" categories,
  # and replace the "other" in the school variable with the grouped other categories
  mutate(school_selfenter_g = case_when(school_selfenter=="Gallatin School of Individualized Study" ~ "Gallatin",
                                        school_selfenter=="NYU Student Health Center" ~ "Student Health Center",
                                        TRUE ~ school_selfenter),
         
         school = ifelse(school=="other", school_selfenter_g, school)) %>%

  # Compute the number of participants of each school
  group_by(school) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  arrange(-n)

n_schools = dim(schools)[[1]]
```

In the Spring of 2020, the Data Sciences and Software Services (DS3) group at NYU distributed a survey to assess the current needs and use of statisticians and software engineers across the university. As to date, `r n_participant`  participants have responded representing affiliations with `r n_schools` schools or centers across the university.

# Statistical Methodology Results

```{r include = FALSE}
# Group the "Other" categories 
# and replace the "Other" in the stat_need variable with the grouped other categories
stat <- stat %>%
  mutate(stat_need_selfenter_g = case_when(stat_need_selfenter %in% c("None", "none of the above") ~ "",
                                           stat_need_selfenter %in% c("large scale simulations") ~ "Simulation", 
                                           stat_need_selfenter %in% c("otherstat") ~ "Other", 
                                           TRUE ~ stat_need_selfenter)) %>%
         
         mutate(stat_need = ifelse(stat_need %in% c("Other", ""), stat_need_selfenter_g, stat_need))  


stat_needs <- stat %>%
  
  # Select relevant variables and drop rows with missing stat_need
  select(id, stat_need) %>%
  filter(stat_need != "") %>%

  # Compute the number of participants of each statistical methodology
  group_by(stat_need) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  arrange(-n) %>%
  
  mutate(stat_need = capital(stat_need))

n_statneed = dim(stat_needs)[[1]]

```

With regards to statistical needs, respondents indicated that they needed assistance with `r n_statneed` areas of statistics. The following table displays these areas along with the number of respondents who indicated this need.

```{r, echo=FALSE}
# Table and barplot
freq_table(stat_needs[, c("stat_need", "n")], "Statistical Methodology", caption = "Statistical Methodology in Need")
```

```{r, echo = F}

# FTE needed
stat_FTE_needs <- other %>%
  filter(!is.na(stat_FTE_need)) %>%
  mutate(stat_FTE_need = factor(stat_FTE_need)) %>%
  group_by(stat_FTE_need) %>%
  summarise(N = n()) %>%
  ## weighted sum
  mutate(ws = sum(as.numeric(as.character(stat_FTE_need)) * N))


# FTE supported
stat_FTE_supports <- other %>%
  filter(!is.na(stat_FTE_support)) %>%
  mutate(stat_FTE_support = factor(stat_FTE_support)) %>%
  group_by(stat_FTE_support) %>%
  summarise(N = n()) %>%
  ## weighted sum
  mutate(ws = sum(as.numeric(as.character(stat_FTE_support)) * N))

d = data.frame(FTE_Needed = stat_FTE_needs$ws[1], FTE_Supported = stat_FTE_supports$ws[1],
           Needs_Supports_Gap = stat_FTE_needs$ws[1] - stat_FTE_supports$ws[1],
           Pct_Needs_Supported = paste0(round(stat_FTE_supports$ws[1] / stat_FTE_needs$ws[1] * 100, 1), "%")) 

```


In order to better understand the extent of these needs, respondents were asked to indicate the number of full time equivalent (FTE) personnel that they could currently support, and the number they needed to satisfy their research needs across their projects. The following table presents the research needs we observed. Therefore, we observed that among our sample of `r n_participant` respondents, a total of `r d$Pct_Needs_Supported` of needs were currently met. 


```{r, echo=F}
data.frame(FTE_Needed = stat_FTE_needs$ws[1], FTE_Supported = stat_FTE_supports$ws[1],
           Needs_Supports_Gap = stat_FTE_needs$ws[1] - stat_FTE_supports$ws[1],
           Pct_Needs_Supported = paste0(round(stat_FTE_supports$ws[1] / stat_FTE_needs$ws[1] * 100, 1), "%"))  %>%
  kable(booktabs = T,
        caption = "Gap Between Statistical FTE Needed and FTE Supported", col.names = c("FTE Needed", "FTE Supported", "Needs & Supports Gap", "% of Needs Supported"), row.names = F) %>%
    kable_styling(latex_options = "striped") %>%
    kable_styling(latex_options = "HOLD_position") %>%
    row_spec(0, bold = T)
```

The following two tables display respondents opinions on their ability to support their statistical methodology needs through their grants, and whether they would feel comfortable contracting statistical services from a university pool. Of `r n_participant` participants in the survey, `r sum(table(other$stat_opinion_support)[3:5])` indicated that they needed help supporting or locating skilled individuals to meet their statistical needs.

```{r, echo=F}
freq_table(other$stat_opinion_support, "Opinion", 
           transform = T, width_col1 = "15cm",
           caption = "Supporting Statistical Methodology Needs Through Grants")

```

Similarly, the next table shows that `r sum(table(other$stat_univers_pool)[3:4])` respondents indicated interest in contracting a statistical methodologist through a university pool.
```{r, echo=F}
freq_table(other$stat_univers_pool, "Opinion", 
           transform = T, width_col1 = "15cm",
           caption = "Contracting Statistical Methodology Services From a University Pool")

```

```{r, echo = F}
stat_accesses <- other %>%
  
  select(id, stat_access, stat_access_other_specify) %>%
  
  # Unnest the accesses
  unnest_tokens(output = stat_access, input = stat_access, token = 'regex', pattern=",", to_lower = FALSE) %>%
  
  # Group the "other" categories 
  mutate(stat_access_other_specify_g = case_when(
    stat_access_other_specify %in% c("Do it myself", "I'm a biostatistician") ~ "Do it myself",
    stat_access_other_specify %in% c("Consult within the school") ~ "Consult / hire within school",
    TRUE ~ stat_access_other_specify
    )) %>%
  
  # Replace the category of other
  mutate(stat_access = ifelse(stat_access=="Other (Please specify which:)", stat_access_other_specify_g, stat_access),
         stat_access = ifelse(stat_access=="Seek consultation from outside the university (Please specify which:)", "Seek consultation from outside the university", stat_access)) %>%
  
  # Compute the number of participants of each access
  group_by(stat_access) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  filter(stat_access != "") %>%
  arrange(-n) %>%
  
  # Capitalize the first letter
  mutate(stat_access = capital(stat_access, word1_only = T))
```

When asked about how they currently access statistical methodology help, `r stat_accesses$n[stat_accesses$stat_access == "Seek consultation from outside the university"]` respondents indicated that they currently seek consultation from outside the university. Furthermore, `r table(other$stat_need_reason)[2]` respondents indicated that the reason they needed help with statistical methodology was to implement innovative methods that could help push forward their research in ways they currently were unable to do themselves.

# Software Engineering Results

```{r, include = F}
# FTE needed
soft_FTE_needs <- other %>%
  filter(!is.na(soft_FTE_need)) %>%
  mutate(soft_FTE_need = factor(soft_FTE_need)) %>%
  group_by(soft_FTE_need) %>%
  summarise(N = n()) %>%
  ## weighted sum
  mutate(ws = sum(as.numeric(as.character(soft_FTE_need)) * N))
```


```{r, echo=FALSE}
# Group the "Other" categories 
# and replace the "Other" in the soft_need variable with the grouped other categories
soft <- soft %>%
  mutate(soft_need_selfenter_g = case_when(soft_need_selfenter %in% c("none", "none of the above") ~ "",
                                           soft_need_selfenter == "Spark and Hadoop tools programming" ~ "Spark & Hadoop",
                                           TRUE ~ soft_need_selfenter)) %>%
  
  mutate(soft_need = ifelse(soft_need %in% c("Other", ""), soft_need_selfenter_g, soft_need))


# Prepare the frequency data frame
soft_needs <- soft %>%
  
  # Select relevant variables and drop rows with missing soft_need
  select(id, soft_need) %>%
  filter(soft_need != "") %>%

  # Compute the number of participants of each school
  group_by(soft_need) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  arrange(-n) %>%
  
  mutate(soft_need = capital(soft_need))

n_softneed = dim(soft_needs)[[1]]

```

A similar investigation of needs pertaining to Software Engineering was conducted. Respondents indicated that they needed assistance with `r n_softneed` areas of software engineering. The following table displays these areas along with the number of respondents who indicated this need.

```{r, echo = F}
# Frequency table

freq_table(soft_needs[, c("soft_need", "n")], "Software Engineering", caption = "Software Engineering in Need")
```

```{r, include = F}
freq_table(soft_FTE_needs[, 1:2], "FTE", caption = "FTE Needed for Software Engineering") %>%
  footnote(general = paste(soft_FTE_needs$ws[1], " FTE needed"),
  general_title = "Total: ", 
  footnote_as_chunk = T, title_format = c("italic", "underline"))



# FTE supported
soft_FTE_supports <- other %>%
  filter(!is.na(soft_FTE_support)) %>%
  mutate(soft_FTE_support = factor(soft_FTE_support)) %>%
  group_by(soft_FTE_support) %>%
  summarise(N = n()) %>%
  ## weighted sum
  mutate(ws = sum(as.numeric(as.character(soft_FTE_support)) * N))

freq_table(soft_FTE_supports[, 1:2], "FTE", caption = "FTE Supported for Software Engineering") %>%
  footnote(general = paste(soft_FTE_supports$ws[1], " FTE supported"),
  general_title = "Total: ", 
  footnote_as_chunk = T, title_format = c("italic", "underline"))

```

```{r, echo = F}
d_soft = data.frame(FTE_Needed = soft_FTE_needs$ws[1], FTE_Supported = soft_FTE_supports$ws[1],
           Needs_Supports_Gap = soft_FTE_needs$ws[1] - soft_FTE_supports$ws[1],
           Pct_Needs_Supported = paste0(round(soft_FTE_supports$ws[1] / soft_FTE_needs$ws[1] * 100, 1), "%")) 
```

In order to better understand the extent of these needs, respondents were asked to indicate the number of FTE personnel that they could currently support, and the number they needed to satisfy their research needs across their projects. The following table presents the research needs we observed. Therefore, we observed that among our sample of `r n_participant` respondents, a total of `r d_soft$Pct_Needs_Supported` of needs were currently met.

```{r, echo=F}
data.frame(FTE_Needed = soft_FTE_needs$ws[1], FTE_Supported = soft_FTE_supports$ws[1],
           Needs_Supports_Gap = soft_FTE_needs$ws[1] - soft_FTE_supports$ws[1],
           Pct_Needs_Supported = paste0(round(soft_FTE_supports$ws[1] / soft_FTE_needs$ws[1] * 100, 1), "%")) %>%
  kable(booktabs = T,
        caption = "Gap Between Software FTE Needed and FTE Supported", col.names = c("FTE Needed", "FTE Supported", "Needs & Supports Gap", "% of Needs Supported"), row.names = F) %>%
    kable_styling(latex_options = "striped") %>%
    kable_styling(latex_options = "HOLD_position") %>%
    row_spec(0, bold = T)
```
 
The following two tables display respondents opinions on their ability to support their software engineering needs through their grants, and whether they would feel comfortable contracting such services from a university pool. Of `r n_participant` participants in the survey, `r sum(table(other$soft_opinion_support)[3:5])` indicated that they needed help supporting or locating skilled individuals to meet their software needs.

```{r, echo=F}
freq_table(other$soft_opinion_support, "Opinion", 
           transform = T, width_col1 = "15cm",
           caption = "Supporting Software Engineering Needs Through Grants")

```

Similarly, the next table shows that `r sum(table(other$soft_univers_pool)[3:4])` respondents indicated interest in contracting a software engineer through a university pool.

```{r, echo=F}
freq_table(other$soft_univers_pool, "Opinion", 
           transform = T, width_col1 = "15cm",
           caption = "Contracting software engineering services from a university pool")

```

```{r, echo = F}
soft_accesses <- other %>%
  
  select(id, soft_access, soft_access_other_specify) %>%
  
  # Unnest the accesses
  unnest_tokens(output = soft_access, input = soft_access, token = 'regex', pattern=",", to_lower = FALSE) %>%
  
  # Group the "other" categories 
  mutate(soft_access_other_specify_g = case_when(grepl("myself", tolower(soft_access_other_specify)) | grepl("personally", tolower(soft_access_other_specify)) ~ "Do it myself",
                                                 #soft_access_other_specify == "Personally and through students" ~ "Do it myself",
                                                 soft_access_other_specify %in% c("Current research programmer, who will only be on staff for a year", "hire a software engineer", "Hire a staff member") ~ "Hire software staff",
                                                 grepl("postdoc", tolower(soft_access_other_specify)) ~ "Postdocs",
                                                 TRUE ~ soft_access_other_specify)) %>%
  # Replace the category of other
  mutate(soft_access_other_specify_g =  case_when(
    soft_access_other_specify %in% c("Do it myself") ~ "Do it myself",
    soft_access_other_specify %in% c("hire a software engineer") ~ "Hire software staff",
    soft_access_other_specify == "other1" ~ "Other",
    TRUE ~ soft_access_other_specify
    )) %>%
  
  # Compute the number of participants of each access
  group_by(soft_access) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  
  # Arrange by the number of participants
  filter(soft_access != "") %>%
  arrange(-n) %>%
  
  # Capitalize the first letter
  mutate(soft_access = capital(soft_access, word1_only = T))
```

When asked about how they currently access software engineering help, `r soft_accesses$n[soft_accesses$soft_access == "Seek consultation from outside the university"]` respondents indicated that they currently seek consultation from outside the university. The places from where these consultations were solicited included hiring independent developers. Furthermore, `r table(other$soft_need_reason)[2]` respondents indicated that the reason they needed help with software engineering was to implement innovative methods that could help push forward their research in ways they currently were unable to do themselves.

# Testimonials

``This is a decoy comment.''